\documentclass[11pt]{letter}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\signature{Mohammed Mohaisen}
\address{Mohammed Mohaisen\\
Department of Artificial Intelligence and Systems Engineering\\
Budapest University of Technology and Economics\\
Budapest, Hungary\\
\href{mailto:mohammed.mohaisen@edu.bme.hu}{mohammed.mohaisen@edu.bme.hu}}

\begin{document}
\begin{letter}{Editor\\
BMC Medical Imaging\\
Springer Nature}

\opening{Dear Editor,}

We are pleased to submit our manuscript entitled \emph{``Validation-Locked Attribution Fingerprints for Auditable Domain-Shift Monitoring in Chest X-ray Segmentation''} for consideration in \emph{BMC Medical Imaging}.

This work presents a reviewer-traceable framework for domain-shift monitoring in chest X-ray segmentation that combines attribution fingerprints, explicit validation gates, robust multi-metric auditing, and a validation-locked decision process. The manuscript's primary evidence is a 20-seed Phase 1 Extended evaluation with strong endpoint-specific operating results and auditable deployment interpretation. In addition, we include an attempted hardshift extension that failed under predeclared validation criteria and is reported as an honest negative result rather than a post hoc positive claim.

We believe this manuscript is well aligned with \emph{BMC Medical Imaging} because it emphasizes methodological transparency, reproducibility, and clinically relevant evaluation in medical image analysis. The paper's key value lies not only in the primary positive result, but also in the explicit audit trail that constrains overclaiming and documents the method's current boundary in a harder setting. This framing matches the journal's emphasis on scientifically sound, clearly documented medical-imaging research.

The manuscript is original, has not been published previously, and is not under consideration elsewhere. All authors have approved the submission. All analyses were conducted on publicly available de-identified datasets, and no additional ethics approval was required.

The code, configurations, governance manifests, and reproducibility assets are available in our public repository at \url{https://github.com/Mo7aisen/xai-shift-fingerprints}. The submission-aligned repository state corresponds to commit \texttt{55f9ebd} (2026-02-28). We are also providing reviewer-facing supplementary audit materials and freeze manifests as Additional files.

Thank you for considering our submission.

\closing{Sincerely,}

\encl{Manuscript source, figures, bibliography, and reviewer-traceable supplementary materials}

\end{letter}
\end{document}
